---
title: "2_plots"
output: html_document
date: "2023-03-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(deSolve)
library(ggplot2)
library(tidyr)
library(ggpubr)
library(ggmatplot)
library(RColorBrewer)
library(gridExtra)
library(cowplot)
library(viridis)
```

# First section on NNTs
```{r}
nnt_main<- readRDS("0_res/nnt_main_int_hi.RDS")

scen_lab <- data.frame(scen = sort(unique(nnt_main$scen)),
                       scen2= c("ann_late","bi_late",NA,"0.5","0.55","0.6","0.65","0.7","0.75","0.8"),
                       lab1 = c("Annual","Biennial","No vax","50% thresh","55% thresh", "60% thresh", "65% thresh","70% thresh","75% thresh","80% thresh"),
                       lab2 = c("Annual","Biennial","No vax","50%","55%", "60%", "65%","70%","75%","80%"))%>%
  mutate(lab1 = 
    factor(lab1, levels=c("No vax","Annual","Biennial","50% thresh","55% thresh","60% thresh",
              "65% thresh","70% thresh","75% thresh","80% thresh")),
         lab2 = 
    factor(lab2, levels =c("No vax", "Annual", "Biennial","50%", "55%", "60%","65%","70%","75%","80%")))
```


## Summary table
```{r}

tab1 <- nnt_main%>%
  #filter(nnt>0)%>%
  #filter(!sweep_unique %in% nnt_neg_rem)%>%
  group_by(scen)%>%
  summarise(nnt_med=median(nnt,na.rm = T),
            nnt_25 = quantile(nnt,probs=0.25, na.rm = T),
            nnt_75 = quantile(nnt, probs=0.75, na.rm=T),
            nnt_e_med = median(nnt_e, na.rm=T),
            nnt_e_25 = quantile(nnt_e,probs=0.25, na.rm = T),
            nnt_e_75 = quantile(nnt_e, probs=0.75, na.rm=T),
            num_camp_med = median(num_campaigns, na.rm=T),
            num_camp_25 = quantile(num_campaigns, probs=0.25, na.rm=T),
            num_camp_75 = quantile(num_campaigns, probs=0.75, na.rm=T),
            dt_avert_e_med = median(deaths_averted_e, na.rm=T),
            dt_avert_e_25 = quantile(deaths_averted_e, probs=0.25, na.rm=T),
            dt_avert_e_75 = quantile(deaths_averted_e, probs=0.75, na.rm=T),
            dt_avert_med = median(deaths_averted, na.rm=T),
            dt_avert_25 = quantile(deaths_averted, probs=0.25, na.rm=T),
            dt_avert_75 = quantile(deaths_averted, probs=0.75, na.rm=T),
            dt_med = median(num_deaths, na.rm=T),
            dt_25 = quantile(num_deaths, probs=0.25, na.rm=T), 
            dt_75 = quantile(num_deaths, probs=0.75, na.rm=T),
            dt_e_med = median(num_deaths_e, na.rm=T),
            dt_e_25 = quantile(num_deaths_e, probs=0.25, na.rm=T), 
            dt_e_75 = quantile(num_deaths_e, probs=0.75, na.rm=T),
            firstvax_med =median(firstvax, na.rm=T),
            firstvax_25 = quantile(firstvax, probs=0.25, na.rm=T),
            firstvax_75 = quantile(firstvax, probs=0.75, na.rm=T))%>%
            
            #nnt_med_p2 = median(nnt_post2, na.rm=T),
            #nnt_25_p2 = quantile(nnt_post2, probs=0.25, na.rm=T),
            #nnt_75_p2 = quantile(nnt_post2, probs=0.75, na.rm=T)) 
  
  mutate(NNT = paste(round(nnt_med, digits=0)," (", round(nnt_25, digits=0),"-",round(nnt_75, digits=0),")", sep=""),
         NNT_e = paste(round(nnt_e_med, digits=0)," (", round(nnt_e_25, digits=0),"-",round(nnt_e_75, digits=0),")", sep=""),
         NumCampaign = paste(round(num_camp_med, digits=0)," (", round(num_camp_25, digits=0),"-",round(num_camp_75,digits=0),")", sep=""),
         DeathsAverted = paste(round(dt_avert_med, digits=0)," (", round(dt_avert_25, digits=0),"-",round(dt_avert_75, digits=0),")", sep=""),
         DeathsAverted_e = paste(round(dt_avert_e_med, digits=0)," (", round(dt_avert_e_25, digits=0),"-",round(dt_avert_e_75, digits=0),")", sep=""),
         Deaths = paste(round(dt_med, digits=0)," (", round(dt_25, digits=0),"-",round(dt_75, digits=0),")", sep=""),
         Deaths_e = paste(round(dt_e_med, digits=0)," (", round(dt_e_25, digits=0),"-",round(dt_e_75, digits=0),")", sep=""),

         FirstVaxTime = paste(round(firstvax_med)," (",round(firstvax_25),"-",round(firstvax_75),")", sep=""))%>%
         #NNT_post2 = paste(round(nnt_med_p2, digits=0), " (", round(nnt_25_p2, digits=0),"-", round(nnt_75_p2, digits = 0), ")", sep=""))%>%
  
  left_join(scen_lab, by="scen")%>%
  select(lab1, NNT_e, DeathsAverted_e, Deaths_e, NNT, DeathsAverted, Deaths, NumCampaign, DeathsAverted, Deaths,FirstVaxTime)

write.csv(tab1, "0_plot/nnt_interpol_hi.csv")
```

##Compiling time series of cases, seroprev and immunity for facet illustration
## Boxplot
```{r}
png("0_plot/nnt_box_Rrand_hi.png", width = 10,height = 5,units="in",res=400)
nnt_main%>%
  #filter(nnt <=10000 & nnt >0)%>%
  filter(nnt <=10000&nnt >-1000)%>%
  left_join(scen_lab)%>%
  filter(!scen%in%c("No vax"))%>%
  ggplot(aes(x=factor(lab1), y=nnt))+
  geom_boxplot(width=0.5)+
  theme_bw()+
  theme(axis.text.x = element_text(angle=20, vjust=0.8, hjust=0.5, size=11),
        axis.text.y = element_text(size=11),
        axis.title = element_text(size=12),
        plot.title = element_text(size=14))+
  ylab("No. of doses needed to avert one death")+xlab("Vaccination timing")+
  ggtitle("Number of vaccine doses needed to avert one death by vaccination timing strategy")
dev.off()
```

## NNT and deaths for elderly only
```{r}
viridis(20, alpha = 1, begin = 0, end = 1, direction = 1, option = "A")
pal <- c("#201321FF","#3C3162FF","#3B589AFF","#3485A5FF","#3CB2ADFF","#81D8B0FF","#DEF5E5FF","#FCFDBFFF","#FDE4A6FF")
pal1 <- c("#201321FF","#3C3162FF","#3B589AFF","#3485A5FF","#3CB2ADFF","#81D8B0FF","#DEF5E5FF","#FDE4A6FF","#FECC8FFF")

theme_frame <- theme(panel.background = element_rect(fill = "white", colour = "black",size = 0.7, linetype = "solid"),
        panel.grid.major = element_line(size = 0.0001, linetype = 'solid',colour = "white"),
        panel.grid.minor = element_line(size = 0.0001, linetype = 'solid',
                                colour = "white"))

#png("nnt_box_Rrand_lo_violin.png", width = 10,height = 5,units="in",res=400)
p11o <- nnt_main%>%
  filter(nnt_e<=15000 & nnt_e >-1500)%>%
  #filter(nnt_e <=15000)%>%
  left_join(scen_lab)%>%
  filter(!scen%in%c("No vax"))%>%
  ggplot(aes(x=lab2, y=nnt_e, fill=lab2, text=lab2))+
  geom_violin(width=1, size=0.2)+
  scale_fill_manual(values = rev(pal1))+
  scale_color_manual(values=rev(pal1))+
  #scale_fill_viridis(discrete=T, option="G")+
  #scale_color_viridis(discrete=T, option="G")+
  theme_classic()+
  theme(axis.text.x = element_text(vjust=0.8, hjust=0.5, size=11),
        axis.text.y = element_text(size=13),
        axis.title = element_text(size=13),
        plot.title = element_text(size=13),
        legend.position="none")+
  theme_frame+
  coord_flip()+
  ylab("No. of doses needed to avert one death")+xlab("Vaccination timing")+
  ggtitle("Number of vaccine doses needed to avert one death")
#dev.off()

##Age-specific death distribution by vax scenario
age_death <- nnt_main %>%
  left_join(scen_lab)%>%
  #filter(!scen%in%c("No vax"))%>%
  select(lab2, num_deaths_c:num_deaths_e)%>%
  pivot_longer(cols=num_deaths_c:num_deaths_e, names_to="var", values_to="val")%>%
  group_by(lab2,var)%>%
  summarise(death_med=median(val),
            death_25 = quantile(val, probs=0.25),
            death_75 = quantile(val, probs=0.75))%>%
  left_join(data.frame(var =c("num_deaths_c","num_deaths_a","num_deaths_e"),
                       age_grp = c("Child","Adult","Adult >50 yr")))%>%
  mutate(age_grp = factor(age_grp, level=c("Adult >50 yr","Adult","Child")))

death_e <- age_death %>%
        filter(var=="num_deaths_e")

p12o <- death_e%>%
  filter(var=="num_deaths_e")%>%
  ggplot()+
  geom_col(aes(x=lab2,y=death_med), fill="#006D2C", width=0.7, alpha=0.5)+
geom_errorbar(data=death_e, aes(x=lab2, ymin=death_25, ymax=death_75), width=0.3, size=0.7, color="gray50")+
  coord_flip()+
 theme_classic()+
            ylab("Deaths")+xlab("")+ggtitle("10-yr cumulative deaths (older adults)")+
          theme(plot.title = element_text(size=14),
                      axis.text.x = element_text(size=13),
                      axis.text.y = element_text(size=11, hjust=1),
                      axis.title = element_text(size=13),
                     legend.position="none")+
  theme_frame

png("0_plot/res_waninghi_older.png", width = 12,height = 4,units="in",res=500)
as_ggplot(arrangeGrob(p11o,p12o,nrow=1,ncol =6, layout_matrix=rbind(c(1,1,1,2,2,2))))
dev.off()
```

## NNT and age-specific deaths for all age groups
```{r}

#png("nnt_box_Rrand_lo_violin.png", width = 10,height = 5,units="in",res=400)
p11 <- nnt_main%>%
  filter(nnt <=15000 & nnt >-1500)%>%
  left_join(scen_lab)%>%
  filter(!scen%in%c("No vax"))%>%
  ggplot(aes(x=factor(lab2), y=nnt, fill=lab2, text=lab2))+
  geom_violin(width=1, size=0.2)+
  scale_fill_manual(values = rev(pal1))+
  scale_color_manual(values=rev(pal1))+
  #scale_fill_viridis(discrete=T, option="G")+
  #scale_color_viridis(discrete=T, option="G")+
  theme_bw()+
  theme(axis.text.x = element_text(vjust=0.8, hjust=0.5, size=11),
        axis.text.y = element_text(size=11),
        axis.title = element_text(size=12),
        plot.title = element_text(size=12),
        legend.position="none")+
  theme_frame+
  coord_flip()+
  ylab("No. of doses needed to avert one death")+xlab("Vaccination timing")+
  ggtitle("Number of vaccine doses needed to avert one death")
#dev.off()

##Age-specific death distribution by vax scenario
age_death <- nnt_main %>%
  left_join(scen_lab)%>%
  #filter(!scen%in%c("No vax"))%>%
  select(lab2, num_deaths_c:num_deaths_e)%>%
  pivot_longer(cols=num_deaths_c:num_deaths_e, names_to="var", values_to="val")%>%
  group_by(lab2,var)%>%
  summarise(death_med=median(val),
            death_25 = quantile(val, probs=0.25),
            death_75 = quantile(val, probs=0.75))%>%
  left_join(data.frame(var =c("num_deaths_c","num_deaths_a","num_deaths_e"),
                       age_grp = c("Child","Adult","Adult >50 yr")))%>%
  mutate(age_grp = factor(age_grp, level=c("Adult >50 yr","Adult","Child")))

all_death <- nnt_main %>%
        left_join(scen_lab)%>%
        #filter(!scen%in%c("No vax"))%>%
        group_by(lab2)%>%
        summarise(death_25 = quantile(num_deaths, probs=0.25),
                  death_75 = quantile(num_deaths, probs=0.75))

p12 <- age_death%>%
  ggplot()+
  geom_col(aes(x=lab2,y=death_med, fill=age_grp), position= "stack", width=0.7, alpha=0.5)+
  scale_fill_manual(values = c("#006D2C","#66C2A4","#CCECE6"),
                     labels=c("Older \nadults","Adult","Child"))+
geom_errorbar(data=all_death, aes(x=lab2, ymin=death_25, ymax=death_75), width=0.3, size=0.7, color="gray50")+
  coord_flip()+
 theme_classic()+
            ylab("Deaths")+xlab("")+ggtitle("10-yr cumulative deaths")+
          theme(plot.title = element_text(size=12),
                      axis.text.x = element_text(size=11),
                      axis.text.y = element_text(size=11, hjust=1),
                      axis.title = element_text(size=12),
                     legend.position="right", legend.title = element_blank(), legend.text = element_text(size=11))+ theme(plot.margin = unit(c(-0.5,0.5,0,-0.7), 'lines'))+
  theme_frame

png("0_plot/res_waninghi_all.png", width = 12,height = 5,units="in",res=500)
as_ggplot(arrangeGrob(p11,p12,nrow=1,ncol =6, layout_matrix=rbind(c(1,1,1,2,2,2))))
dev.off()
```


##Cases per capita
```{r}
inc <- readRDS("0_res/inc_facet_comb100.RDS")
inc<-inc%>%filter(sero_thresh %in% c("0","0.5","0.65","0.8","Annual", "Biennial"))

med<- inc%>%group_by(date,sero_thresh)%>%
      summarise(med = median(val),
                prob_25 = quantile(val, probs=0.10),
                prob_75 = quantile(val, probs=0.90))

p1 <- med %>% ggplot()+
    geom_ribbon(aes(x=date, ymin=prob_25, ymax=prob_75, fill="Range"))+
     theme_bw()+geom_line(aes(x=date, y=med, colour = "Cases \n per 100"), size=0.6)+  

    scale_colour_manual("",values="#EF3B2C")+
    scale_fill_manual("",values="gray78")+
  #ggtitle("10-year epidemic projection")+
  xlab("") + ylab("Cases per 100")+
  facet_wrap(~sero_thresh, nrow=1)+
    theme(plot.title = element_text(size=14),
                      axis.text.x = element_text(angle=30, vjust=1.2, hjust=1, size=11),
                      axis.text = element_text(size=11),
                      axis.title = element_text(size=12),
                      strip.text = element_blank(),
                      legend.text = element_text(size=12),
        legend.position = "right")+
  theme(plot.margin = unit(c(-0.5,0.2,0,1), 'lines'))+
  theme(panel.background = element_rect(fill = "white", colour = "black",size = 0.7, linetype = "solid"),
        panel.grid.major = element_line(size = 0.001, linetype = 'solid',colour = "white"),
        panel.grid.minor = element_line(size = 0.001, linetype = 'solid',
                                colour = "white"))
png("0_plot/inc_strip.png",width = 12,height = 5,units="in",res=400)
p1
dev.off()


```

## Deaths per capita
```{r}
death <- readRDS("0_res/death_facet_comb100.RDS")
death<-death%>%filter(sero_thresh %in% c("0","0.5","0.65","0.8","Annual", "Biennial"))

med<- death%>%
     mutate(deathpermil = val*10000)%>%
      group_by(date,sero_thresh)%>%
      summarise(med = median(deathpermil),
                prob_25 = quantile(deathpermil, probs=0.10),
                prob_75 = quantile(deathpermil, probs=0.90))

p1 <- med %>% ggplot()+
    geom_ribbon(aes(x=date, ymin=prob_25, ymax=prob_75, fill="Range"))+
     theme_bw()+geom_line(aes(x=date, y=med, colour = "Cases \n per 100"), size=0.6)+  

    scale_colour_manual("",values="#EF3B2C")+
    scale_fill_manual("",values="gray78")+
  #ggtitle("10-year epidemic projection")+
  xlab("") + ylab("Cases per 100")+
  facet_wrap(~sero_thresh, nrow=1)+
    theme(plot.title = element_text(size=14),
                      axis.text.x = element_text(angle=30, vjust=1.2, hjust=1, size=11),
                      axis.text = element_text(size=11),
                      axis.title = element_text(size=12),
                      strip.text = element_blank(),
                      legend.text = element_text(size=12),
        legend.position = "right")+
  theme(plot.margin = unit(c(-0.5,0.2,0,1), 'lines'))+
  theme(panel.background = element_rect(fill = "white", colour = "black",size = 0.7, linetype = "solid"),
        panel.grid.major = element_line(size = 0.001, linetype = 'solid',colour = "white"),
        panel.grid.minor = element_line(size = 0.001, linetype = 'solid',
                                colour = "white"))
png("0_plot/inc_strip.png",width = 12,height = 5,units="in",res=400)
p1
dev.off()

```



## Sero facet wrap
```{r}
sero <- readRDS("0_res/sero_facet_comb100.RDS")
thresh_line <- data.frame(scen=c("No vax","50% thresh", "65% thresh","80% thresh","Annual","Biennial"),
                          sero_thresh = c("0","0.5","0.65","0.8","Annual","Biennial"),
                          thresh_num = c(NA,53,67,81,NA,NA))%>%
              mutate(scen = factor(scen, levels = c("No vax", "50% thresh", "65% thresh", "80% thresh", "Annual","Biennial")))

sero<-sero%>%filter(sero_thresh %in% c("0","0.5","0.65","0.8","Annual","Biennial"))
sero<-sero%>%pivot_longer(cols = sero_c:sero_e, names_to = "sero",values_to="val")

sero_med<- sero%>%group_by(date,sero_thresh,sero)%>%
      summarise(med = median(val),
                prob25 = quantile(val, probs=0.25),
                prob75 = quantile(val, probs=0.75)) %>%
      left_join(thresh_line %>%select(scen, sero_thresh))
sero_range_c <- sero_med %>%filter(sero=="sero_c")
sero_range_a <- sero_med %>%filter(sero=="sero_a")
sero_range_e <- sero_med %>%filter(sero=="sero_e")
                

p2 <-  ggplot()+
      geom_ribbon(data=sero_range_c,aes(x=date, ymin=prob25, ymax=prob75), fill="gray78",alpha=0.5)+
      geom_ribbon(data=sero_range_a,aes(x=date, ymin=prob25, ymax=prob75), fill="gray78", alpha=0.5)+
      geom_ribbon(data=sero_range_e,aes(x=date, ymin=prob25, ymax=prob75), fill="gray78", alpha=0.5)+
      geom_line(data=sero_med,aes(x=date, y = med, col = sero),size=1)+       
      facet_wrap(~scen, nrow=1, scales="fixed")+
      ylim(0,100) +theme_bw()+
      scale_color_manual(values = c("#4292C6","#C6DBEF","#08306B"),
                                   labels=c("Adult",
                                            "Child",
                                            "Older \nadults"))+
        xlab("")+
                theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      axis.text.y = element_text(size=11),
                      strip.text = element_text(size=13),
                      legend.position = "right",legend.title = element_blank(), legend.text = element_text(size=12),
                      plot.margin = unit(c(0,0,-0.5,1), "line"))+
      geom_hline(data=thresh_line,aes(yintercept=thresh_num),linetype="dashed",size=0.6)+
  ylab("Seroprevalence\n by age(%)")+
  theme(panel.background = element_rect(fill = "white", colour = "black",size = 0.7, linetype = "solid"),
        panel.grid.major = element_line(size = 0.00001, linetype = 'solid',colour = "white"),
        panel.grid.minor = element_line(size = 0.00001, linetype = 'solid',
                                colour = "white"))

png("z_sero_strip.png",width = 12,height = 5,units="in",res=400)
p2
dev.off()
```

```{r}
p3 <-ggarrange(p2,p1,ncol=1, align="v")
p4<- ggarrange(p11,p12, ncol=2, align="h")

png("0_plot/fig2_hiescape1.png", width = 11,height = 9,units="in",res=600)
ggarrange(p3, p4,nrow=2, align="v" )
dev.off()

png("0_plot/fig2_hiescape.png", width = 11,height = 9,units="in",res=600)
as_ggplot(arrangeGrob(p3, p11o,p12o, nrow=4,ncol =2, 
                      layout_matrix=rbind(c(1,1), c(1,1),c(2,3),c(2,3))))
dev.off()

p4 <- as_ggplot(arrangeGrob(p11,p12,nrow=1,ncol =6, layout_matrix=rbind(c(1,1,1,2,2))))

ggarrange(p3, p4, ncol=1, align="v")

```

```{r}
imm <- readRDS("0_res/imm_facet_comb100.RDS")
imm<- imm%>%
      pivot_longer(cols =s0v0_c:imm1_e, names_to = "var", values_to="val")%>%
        mutate(age_grp = substr(var, 6,6),
               imm_cat = substr(var, 1,4),
               imm_cat = factor(imm_cat, levels = c("imm1","s0v0","s1v0","s2v0", "s0v2","s1v2","s2v2", "s0v3","s1v3","s2v3")),
               age_grp = factor(age_grp, levels=c("c","a","e")))
#imm<-imm%>%filter(sero_thresh %in% c("0","0.5","0.65","0.8","Annual","Biennial"))

imm_med<- imm%>%group_by(date,sero_thresh,imm_cat, age_grp)%>%
      summarise(med = median(val),
                prob25 = quantile(val, probs=0.25),
                prob75 = quantile(val, probs=0.75))

imm_med <- imm_med %>%
            left_join(data.frame(age_grp = c("a","c","e"),
                                  age_lab = c("Adult","Child","Older adult")))%>%
            left_join(data.frame(sero_thresh = c("0","0.5","0.65","0.8","Annual","Biennial"),
                                 sero_lab = c("No vax","50% thresh", "65% thresh", "80% thresh","Annual","Biennial")))%>%
            mutate(age_lab = factor(age_lab, levels=c("Child","Adult","Older adult")),
                   sero_lab = factor(sero_lab, levels =  c("No vax","50% thresh", "65% thresh", "80% thresh","Annual","Biennial")))

imm_med <- imm_med%>%
            filter(sero_thresh%in%c("0","0.5","0.8","Annual"))

imm_med %>% filter(age_grp=="e"&sero_thresh=="Annual"&date==as.Date("2022-09-1"))
#imm_med %>% filter(age_grp=="e"&sero_thresh=="Biennial"&date==as.Date("2022-09-1"))
imm_med %>% filter(age_grp=="e"&sero_thresh=="0.5"&date==as.Date("2022-09-1"))


p3 <- imm_med%>%ggplot(aes(x=date, y=med, fill=imm_cat))+
          geom_col(aes(x=date, y=med, fill=imm_cat, width=1), position="fill")+
          #scale_fill_manual(values = c("#FFFF99",
                                       #"#A1D99B","#C7E9C0", "#E5F5E0", #Greens
          #                             "#35978F","#80CDC1","#C7EAE5",
          #                             "#6BAED6","#9ECAE1","#DEEBF7",
          #                             "#3690C0","#74A9CF","#A6BDDB"))+
                                      # "#88419D", "#8C96C6","#D0D1E6" ))+
          scale_fill_manual(values = c("#FFFFCC",
                                       "#35978F","#80CDC1","#C7EAE5",
                                       brewer.pal(9, "PuBu")[c(7,6,5,4,3,2)]))+
          facet_grid(rows=vars(sero_lab),cols=vars(age_lab))+theme_classic()+
          xlab("Year") + ylab("Population proportion")+
          #theme(panel.margin = unit(0, "lines")) +
          #theme(plot.margin = unit(c(0,0,0,0), "lines"))+
          theme(axis.text = element_text(size=13),
                      axis.title = element_text(size=15),
                     strip.text = element_text(size=15))

png("0_plot/imm_strip_simp.png",width = 12,height = 14,units="in",res=400)
p3
dev.off()

```
##NNT death tradeoff
```{r}
lab = c("Annual","Biennial","50%","55%", "60%", "65%","70%","75%","80%")

##Main one for output
nnt_death_trade <- nnt_main %>%
  filter(scen!="No vax")%>%
  ggplot(aes(x=num_deaths_e, y=nnt_e, col=scen))+
  scale_fill_manual(values = rev(pal),labels = lab)+
  scale_color_manual(values=rev(pal),labels = lab)+
  #scale_color_viridis(discrete=T, option="G", direction=-1, alpha=1)+
  #scale_fill_viridis(discrete=T, option="G", direction=-1, alpha=0.5)+
  geom_point()+xlim(0,12000)+ylim(0,15000)+
  theme_bw() + xlab("Number of deaths among older adults")+ylab("Number needed to treat (NNT) among older adults")+
  theme(legend.title = element_blank(), legend.position = "none")

## Other explorations
nnt_main %>%
  filter(scen!="No vax")%>%
  ggplot(aes(x=deaths_averted, y=nnt, col=scen))+
  geom_point()+xlim(0,6500)+ylim(0,3000)


nnt_main%>%
  filter(scen!="No vax")%>%
  ggplot(aes(x=num_campaigns, y=nnt, col=scen))+
  geom_point()+ylim(0,3000)

nnt_main%>%
  filter(scen!="No vax")%>%
  ggplot(aes(x=firstvax, y=nnt, col=scen))+
  geom_point()+ylim(0,3000)+xlim(0,2000)

```

## Yearly cumulative NNT
```{r}
viridis(20, alpha = 1, begin = 0, end = 1, direction = 1, option = "A")
pal1 <- c("#201321FF","#3C3162FF","#3B589AFF","#3485A5FF","#3CB2ADFF","#81D8B0FF","#DEF5E5FF","#FDE4A6FF","#FECC8FFF")

nnt_yr <- readRDS("0_res/nnt_main_wanehi_yr_hiescape.RDS")
nnt1_yr<-readRDS("0_res/nnt1_main_wanehi_yr_hiescape.RDS")


nnt_yr <- nnt_yr %>%filter(yr!=10)%>%
  group_by(scenarios, sweep_unique)%>%
  replace(is.na(.),0)%>%
  mutate(num_dose_roll = cumsum(num_dose))
nnt_yr_novax <- nnt_yr %>%filter(scenarios==0)%>%
                  ungroup()%>%
                  select(sweep_unique, yr, new_Deaths_e_roll, new_Deaths_tot_roll)%>%
                  rename("new_Deaths_e_roll_novax"="new_Deaths_e_roll")%>%
                  rename("new_Deaths_tot_roll_novax"="new_Deaths_tot_roll")

nnt_yr <- nnt_yr %>% left_join(nnt_yr_novax, by=c("sweep_unique"="sweep_unique","yr"="yr"))%>%
            mutate(nnt_e_yr = num_dose_roll/(new_Deaths_e_roll_novax-new_Deaths_e_roll),
                   nnt_tot_yr = num_dose_roll/(new_Deaths_tot_roll_novax-new_Deaths_tot_roll))%>%
            filter(scenarios!=0)

nnt1_yr <- nnt1_yr %>%filter(yr!=10)%>%
          group_by(scenarios, sweep_unique)%>%
          replace(is.na(.),0)%>%
          mutate(num_dose_roll = cumsum(num_dose))%>%
            left_join(nnt_yr_novax, by=c("sweep_unique"="sweep_unique", "yr"="yr"))%>%
            mutate(nnt_e_yr = num_dose_roll/(new_Deaths_e_roll_novax-new_Deaths_e_roll),
                   nnt_tot_yr = num_dose_roll/(new_Deaths_tot_roll_novax-new_Deaths_tot_roll))
  
nnt_yr_trade <- nnt_yr %>%
  mutate(scenarios = as.character(scenarios))%>%
  rbind(nnt1_yr)%>%
  mutate(yr1=yr+1)%>%
  group_by(yr1, scenarios)%>%
  dplyr::summarise(med = median(nnt_e_yr, na.rm=T))%>%
   mutate(scenarios = factor(scenarios,
          levels = c("ann_late","bi_late","0.5","0.55","0.6", "0.65","0.7","0.75","0.8")))%>%
  arrange(scenarios)%>%
  ggplot(aes(x=yr1, y=med, col=scenarios))+
  scale_fill_manual(values = rev(pal1),labels = lab)+
  scale_color_manual(values=rev(pal1),labels = lab)+
  scale_x_continuous(breaks = seq(from = 1, to = 10, by = 1))+
  #scale_color_viridis(discrete=T, option="G", direction=-1, alpha=1)+
  geom_line(size=1, linetype="dashed")+
  geom_point(size=2.5)+theme_bw()+
  theme(legend.title=element_blank(),
        legend.position = "none")+
  xlab("Year")+ylab("Cumulative NNT (median)")+ylim(0,15000)

png("0_plot/nnt_trade.png", width = 11,height = 4,units="in",res=600)
as_ggplot(arrangeGrob(nnt_yr_trade, nnt_death_trade,nrow=2,ncol =2, 
                      layout_matrix=rbind(c(1,2), c(1,2))))
dev.off()


```


## Correlation between immune/serology metric and cumulative cases
Extract prop at the start of each wave for exposure, outcome is cumulative deaths in the wave
```{r}
start_wave <- inc[1:365,]%>%mutate(prop_inc = val/lag(val))

max(start_wave$prop_inc, na.rm=t)

inc_time <- data.frame(sn = seq(from=0,to=9, by=1),
                       wave= seq(from=1,to=10, by=1))%>%
            mutate(time= sn*365+199)

age_dist <- data.frame(age = c("c","a","e"),
                        pop = c(10884513+4883969, 7958844+4900719, 992149+446454))



inc%>%filter(sweep_unique==201&sero_thresh==0)%>%
  ggplot()+
  geom_line(aes(x=time, y = val),size=1)+
  geom_vline(aes(xintercept = time), inc_time)

## deaths per wave
death_wave <- death%>%mutate(
  wave = case_when(time<inc_time$time[1]~NA_real_,
                   time<inc_time$time[2]~1,
                   time<inc_time$time[3]~2,
                   time<inc_time$time[4]~3,
                   time<inc_time$time[5]~4,
                   time<inc_time$time[6]~5,
                   time<inc_time$time[7]~6,
                   time<inc_time$time[8]~7,
                   time<inc_time$time[9]~8,
                   time<inc_time$time[10]~9,
                   TRUE~10)
)%>%
  group_by(sweep_unique, sero_thresh, wave)%>%
  summarise(tot_death = sum(val),
            peak_death = max(val))

##seroprev per wave
sero_wave <- sero%>%mutate(
  wave = case_when(time<inc_time$time[1]~NA_real_,
                   time<inc_time$time[2]~1,
                   time<inc_time$time[3]~2,
                   time<inc_time$time[4]~3,
                   time<inc_time$time[5]~4,
                   time<inc_time$time[6]~5,
                   time<inc_time$time[7]~6,
                   time<inc_time$time[8]~7,
                   time<inc_time$time[9]~8,
                   time<inc_time$time[10]~9,
                   TRUE~10)
)%>%
  group_by(sweep_unique, sero_thresh, wave, sero)%>%
  slice(1) %>%
  pivot_wider(names_from = "sero", values_from = "val")

## immunity per wave
sus_val <- data.frame(imm_cat = unique(imm$imm_cat),
                      sus_val = c(1,0.54,0.23,0.62,0.33,0.14,0.46,0.25,0.1,0))

imm_wave <- imm %>% filter(time %in% unlist(inc_time$time))
imm_wave <- imm_wave%>% left_join(
  sus_val, by = c("imm_cat"="imm_cat")
)

##Made an error with summing up the sus in children.. need to figure out a quick proxy without rerunning all the models
imm_wave1 <- imm_wave%>%
            select(-sus_val, -var)%>%
            pivot_wider(names_from = "imm_cat", values_from="val")%>% 
            replace_na(list(s0v2 = 0, s1v2=0, s2v2=0, s0v3=0, s1v3=0, s2v3=0))%>%
             mutate(
            sus_tot = s0v0+s1v0+s2v0+s0v2+s1v2+s2v2+s0v3+s1v3+s2v3) %>% 
            left_join(age_dist, by = c("age_grp"="age"))%>%
            mutate(tot = sus_tot+imm1)

imm_wave2<- imm_wave %>% mutate(
  sus_pop = val*sus_val
)%>%
  select(-sus_val, -val,-var)%>%
  replace_na(list(sus_pop = 0))%>%
  pivot_wider(names_from = "imm_cat", values_from="sus_pop")%>% 
    replace_na(list(s0v2 = 0, s1v2=0, s2v2=0, s0v3=0, s1v3=0, s2v3=0))%>%

  mutate(
  sus_tot = s0v0+s1v0+s2v0+s0v2+s1v2+s2v2+s0v3+s1v3+s2v3) %>% 
  left_join(imm_wave1%>%select(time,sweep_unique,sero_thresh,age_grp, tot), 
            by = c("age_grp"="age_grp","time"="time","sweep_unique"="sweep_unique","sero_thresh"="sero_thresh")) %>% 
  mutate(prop_sus = sus_tot/tot)

imm_wave_simp <- imm_wave2%>%
                  select(time, sweep_unique, sero_thresh, age_grp, prop_sus)%>%
                  pivot_wider(names_from = "age_grp", values_from = "prop_sus")%>%
                  left_join(inc_time)



```

## Correlation between seroprevalence and susceptible prop
```{r}
df_corr <- death_wave%>%
  left_join(
  sero_wave%>%select(-time, -date), 
  by = c("wave"="wave","sweep_unique"="sweep_unique","sero_thresh"="sero_thresh")
)%>%
  left_join(
   imm_wave_simp%>%select(-time, -sn),
   by = c("wave"="wave","sweep_unique"="sweep_unique","sero_thresh"="sero_thresh")
  )

df_corr<- df_corr%>% filter(!is.na(wave))
```


```{r}
df_corr <- death_wave%>%
  left_join(
  sero_wave%>%select(-time, -date), 
  by = c("wave"="wave","sweep_unique"="sweep_unique","sero_thresh"="sero_thresh")
)%>%
  left_join(
   imm_wave_simp%>%select(-time, -sn),
   by = c("wave"="wave","sweep_unique"="sweep_unique","sero_thresh"="sero_thresh")
  )

df_corr<- df_corr%>% filter(!is.na(wave))
```



```{r}
theme_text <-theme(axis.text.x = element_text(vjust=0.8, hjust=0.5, size=13),
        axis.text.y = element_text(size=13),
        axis.title = element_text(size=13),
        plot.title = element_text(size=13))

df_corr <- df_corr%>%
            mutate(sero_a=sero_a/100,
                   sero_c=sero_c/100,
                   sero_e=sero_e/100)

df_corr <- df_corr%>%
            mutate(Year=wave)
df_corr_novax <- df_corr %>% filter(sero_thresh==0)
##Monotonic visualization
corr1 <- df_corr %>%filter(sero_thresh==0& wave!=1)%>%
  ggplot(aes(x=e, y=tot_death, col = as.factor(Year)))+
  geom_point()+ 
  #stat_cor(p.accuracy = 0.001, r.accuracy = 0.01)+
  #geom_text(aes(x=-Inf,y=Inf,hjust=0,vjust=1,label=paste("R-squared =",cor(df_corr_novax$tot_death, df_corr_novax$e))), colour="black")+
  ggtitle("Immunity vs deaths among older adults")+
  scale_color_brewer(palette="RdPu", direction=-1, name="Year")+
  theme_classic()+
  theme_text+
  ylab("Deaths per 10,000")+xlab("Population-level proportion susceptible")

corr2 <- df_corr %>%filter(sero_thresh==0& wave!=1)%>%
  ggplot(aes(x=sero_e, y=tot_death, col = as.factor(Year)))+
  geom_point()+
  ggtitle("Seroprevalence vs deaths among older adults")+
  scale_color_brewer(palette="YlGnBu", direction=-1, name="Year")+
  theme_classic()+theme_text+
  ylab("Deaths per 10,000")+xlab("Seroprevalence")+
  theme(legend.title=NULL)

corr3 <- df_corr %>%filter(sero_thresh==0&wave!=1)%>%
  ggplot(aes(x=sero_e, y=e,col=as.factor(Year)))+
  geom_point()+
  ggtitle("Immunity vs seroprevalence among older adults")+
  scale_color_brewer(palette="YlGn", direction=-1,name="Year")+
  theme_classic()+theme_text+
  ylab("Population-level proportion susceptible")+xlab("Seroprevalence")+
  theme(legend.position=NULL)


png("0_plot/corrs.png", width = 5,height = 12,units="in",res=600)
as_ggplot(arrangeGrob(corr2,corr1,corr3,nrow=3,ncol =1)) 
                      #layout_matrix=rbind(1,2,3)))
dev.off()


cor(df_corr_novax$tot_death, df_corr_novax$e)
cor(df_corr_novax$tot_death, df_corr_novax$c)
cor(df_corr_novax$tot_death, df_corr_novax$a)

cor(df_corr_novax$tot_death, df_corr_novax$sero_e)
cor(df_corr_novax$tot_death, df_corr_novax$sero_c)
cor(df_corr_novax$tot_death, df_corr_novax$sero_a)

cor(df_corr_novax$e, df_corr_novax$sero_e)
cor(df_corr_novax$a, df_corr_novax$sero_a)
cor(df_corr_novax$c, df_corr_novax$sero_c)



```



