---
title: "2_plots"
output: html_document
date: "2023-03-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(deSolve)
library(ggplot2)
library(tidyr)
library(ggpubr)
library(ggmatplot)
library(RColorBrewer)
library(gridExtra)
library(cowplot)
library(viridis)
```

# First section on NNTs
```{r}
nnt_main<- readRDS("0_res/1_nnt_main_sens.RDS")

scen_lab <- data.frame(scen = sort(unique(nnt_main$scen)),
                       scen2= c("ann_late","bi_late",NA,"0.5","0.55","0.6","0.65","0.7","0.75","0.8"),
                       lab1 = c("Annual","Biennial","No vax","50% thresh","55% thresh", "60% thresh", "65% thresh","70% thresh","75% thresh","80% thresh"),
                       lab2 = c("Annual","Biennial","No vax","50%","55%", "60%", "65%","70%","75%","80%"))%>%
  mutate(lab1 = 
    factor(lab1, levels=c("No vax","Annual","Biennial","50% thresh","55% thresh","60% thresh",
              "65% thresh","70% thresh","75% thresh","80% thresh")),
         lab2 = 
    factor(lab2, levels =c("No vax", "Annual", "Biennial","50%", "55%", "60%","65%","70%","75%","80%")))

```


## Summary table
```{r}

tab1 <- nnt_main%>%
  filter(nnt_e>0&nnt_e<50000)%>%
  #filter(!sweep_unique %in% nnt_neg_rem)%>%
  group_by(scen)%>%
  dplyr::summarise(nnt_med=median(nnt,na.rm = T),
            nnt_25 = quantile(nnt,probs=0.025, na.rm = T),
            nnt_75 = quantile(nnt, probs=0.975, na.rm=T),
            nnt_e_med = median(nnt_e, na.rm=T),
            nnt_e_25 = quantile(nnt_e,probs=0.025, na.rm = T),
            nnt_e_75 = quantile(nnt_e, probs=0.975, na.rm=T),
            num_camp_med = median(num_campaigns, na.rm=T),
            num_camp_25 = quantile(num_campaigns, probs=0.025, na.rm=T),
            num_camp_75 = quantile(num_campaigns, probs=0.975, na.rm=T),
            dt_avert_e_med = median(deaths_averted_e, na.rm=T),
            dt_avert_e_25 = quantile(deaths_averted_e, probs=0.025, na.rm=T),
            dt_avert_e_75 = quantile(deaths_averted_e, probs=0.975, na.rm=T),
            dt_avert_med = median(deaths_averted, na.rm=T),
            dt_avert_25 = quantile(deaths_averted, probs=0.025, na.rm=T),
            dt_avert_75 = quantile(deaths_averted, probs=0.975, na.rm=T),
            dt_med = median(num_deaths, na.rm=T),
            dt_25 = quantile(num_deaths, probs=0.025, na.rm=T), 
            dt_75 = quantile(num_deaths, probs=0.975, na.rm=T),
            dt_e_med = median(num_deaths_e, na.rm=T),
            dt_e_25 = quantile(num_deaths_e, probs=0.025, na.rm=T), 
            dt_e_75 = quantile(num_deaths_e, probs=0.975, na.rm=T),
            firstvax_med =median(firstvax, na.rm=T),
            firstvax_25 = quantile(firstvax, probs=0.025, na.rm=T),
            firstvax_75 = quantile(firstvax, probs=0.975, na.rm=T))%>%
            
            #nnt_med_p2 = median(nnt_post2, na.rm=T),
            #nnt_25_p2 = quantile(nnt_post2, probs=0.25, na.rm=T),
            #nnt_75_p2 = quantile(nnt_post2, probs=0.75, na.rm=T)) 
  
  mutate(NNT = paste(round(nnt_med, digits=0)," (", round(nnt_25, digits=0),"-",round(nnt_75, digits=0),")", sep=""),
         NNT_e = paste(round(nnt_e_med, digits=0)," (", round(nnt_e_25, digits=0),"-",round(nnt_e_75, digits=0),")", sep=""),
         NumCampaign = paste(round(num_camp_med, digits=0)," (", round(num_camp_25, digits=0),"-",round(num_camp_75,digits=0),")", sep=""),
         DeathsAverted = paste(round(dt_avert_med, digits=0)," (", round(dt_avert_25, digits=0),"-",round(dt_avert_75, digits=0),")", sep=""),
         DeathsAverted_e = paste(round(dt_avert_e_med, digits=0)," (", round(dt_avert_e_25, digits=0),"-",round(dt_avert_e_75, digits=0),")", sep=""),
         Deaths = paste(round(dt_med, digits=0)," (", round(dt_25, digits=0),"-",round(dt_75, digits=0),")", sep=""),
         Deaths_e = paste(round(dt_e_med, digits=0)," (", round(dt_e_25, digits=0),"-",round(dt_e_75, digits=0),")", sep=""),

         FirstVaxTime = paste(round(firstvax_med)," (",round(firstvax_25),"-",round(firstvax_75),")", sep=""))%>%
         #NNT_post2 = paste(round(nnt_med_p2, digits=0), " (", round(nnt_25_p2, digits=0),"-", round(nnt_75_p2, digits = 0), ")", sep=""))%>%
  
  left_join(scen_lab, by="scen")%>%
  select(lab1, NNT_e, DeathsAverted_e, Deaths_e, NNT, DeathsAverted, Deaths, NumCampaign, DeathsAverted, Deaths,FirstVaxTime)

write.csv(tab1, "0_plot/nnt_interpol_hi_95.csv")

tab1
## res for children and adults
nnt_main%>%
  #filter(nnt>0)%>%
  #filter(!sweep_unique %in% nnt_neg_rem)%>%
  group_by(scen)%>%
  dplyr::summarise(
            dt_c_med = median(num_deaths_c, na.rm =T),
            dt_c_25 = quantile(num_deaths_c, probs=0.025, na.rm=T), 
            dt_c_75 = quantile(num_deaths_c, probs=0.975, na.rm=T),
            dt_a_med = median(num_deaths_a, na.rm=T),
            dt_a_25 = quantile(num_deaths_a, probs=0.025, na.rm=T), 
            dt_a_75 = quantile(num_deaths_a, probs=0.975, na.rm=T))

nnt_main %>% 
  filter(nnt>2000)

nnt_main%>%
  group_by(sero_thresh)%>%
  summarise(nnt_top90 = quantile(nnt, probs=0.75, na.rm=T))

nnt_main%>%
  filter(nnt>30000)%>%
  group_by(scen)%>%
  summarise(n=n())

nnt_main%>%
  filter(nnt_e>50000)%>%
  group_by(scen)%>%
  summarise(n=n())

```

##Compiling time series of cases, seroprev and immunity for facet illustration
## Boxplot
```{r}
png("0_plot/nnt_box_Rrand_hi.png", width = 10,height = 5,units="in",res=400)
nnt_main%>%
  #filter(nnt <=10000 & nnt >0)%>%
  #filter(nnt <=10000&nnt >-1000)%>%
  left_join(scen_lab)%>%
  filter(!scen%in%c("No vax"))%>%
  ggplot(aes(x=factor(lab1), y=nnt))+
  scale_y_log10()+
  geom_boxplot(width=0.5)+
  theme_bw()+
  theme(axis.text.x = element_text(angle=20, vjust=0.8, hjust=0.5, size=11),
        axis.text.y = element_text(size=11),
        axis.title = element_text(size=12),
        plot.title = element_text(size=14))+
  ylab("No. of doses needed to avert one death")+xlab("Vaccination timing")+
  ggtitle("Number of vaccine doses needed to avert one death by vaccination timing strategy")
dev.off()
```

## NNT distributions (different visualization)
```{r}
viridis(20, alpha = 1, begin = 0, end = 1, direction = 1, option = "A")
pal <- c("#201321FF","#3C3162FF","#3B589AFF","#3485A5FF","#3CB2ADFF","#81D8B0FF","#DEF5E5FF","#FCFDBFFF","#FDE4A6FF")
pal1 <- c("#201321FF","#3C3162FF","#3B589AFF","#3485A5FF","#3CB2ADFF","#81D8B0FF","#DEF5E5FF","#FDE4A6FF","#FECC8FFF")

theme_frame <- theme(panel.background = element_rect(fill = "white", colour = "black",size = 0.7, linetype = "solid"),
        panel.grid.major = element_line(size = 0.0001, linetype = 'solid',colour = "white"),
        panel.grid.minor = element_line(size = 0.0001, linetype = 'solid',
                                colour = "white"))


p99 <- nnt_main%>%
  select(nnt_e,scen)%>%
  filter(!scen%in%c("No vax","serothresh-0.75"))%>%
  ggplot(aes(x=nnt_e, fill=scen))+geom_density(alpha=0.5)+
  scale_x_log10()+xlim(0,10000)+
  scale_fill_manual(values = rev(pal1))+
  theme_bw()
```

## Probability of serothresholds being more efficient than annual/biennial
```{r}
nnt_main%>%
  filter(scen!="No vax")%>%
  select(nnt_e,sweep_unique,scen)%>%
  pivot_wider(names_from = "scen",values_from="nnt_e")%>%
  pivot_longer(cols=`serothresh-0.5`:`serothresh-0.8`, names_to="serothresh",values_to="nnt_e")%>%
  mutate(prob_eff_ann = ifelse(nnt_e<ann_late,1,0),
         prob_eff_bi = ifelse(nnt_e<bi_late,1,0))%>%
  group_by(serothresh)%>%
  summarise(prob_eff_an= sum(prob_eff_ann)/100,
            prob_eff_bi = sum(prob_eff_bi)/100)
```


## NNT and deaths for elderly only
```{r}

#png("nnt_box_Rrand_lo_violin.png", width = 10,height = 5,units="in",res=400)
p11o <- nnt_main%>%
  #filter(nnt_e<=15000 & nnt_e >-1500)%>%
  #filter(nnt_e <=15000)%>%
  left_join(scen_lab)%>%
  filter(!scen%in%c("No vax"))%>%  
  ggplot(aes(x=lab2, y=nnt_e, fill=lab2, text=lab2))+
  geom_violin(width=1, size=0.2)+
  scale_fill_manual(values = rev(pal1))+
  scale_color_manual(values=rev(pal1))+
  #scale_fill_viridis(discrete=T, option="G")+
  #scale_color_viridis(discrete=T, option="G")+
  ylim(0,30000)+
  scale_y_log10()+
 theme_classic()+
  theme(axis.text.x = element_text(vjust=0.8, hjust=0.5, size=13),
        axis.text.y = element_text(size=13),
        axis.title = element_text(size=13),
        plot.title = element_text(size=13),
        legend.position="none")+
  theme_frame+
  coord_flip()+
  ylab("No. of doses needed to avert one death")+xlab("Vaccination timing")+
  ggtitle("Number of vaccine doses needed to avert one death")
#dev.off()

##Age-specific death distribution by vax scenario
age_death <- nnt_main %>%
  left_join(scen_lab)%>%
  #filter(!scen%in%c("No vax"))%>%
  select(lab2, num_deaths_c:num_deaths_e)%>%
  pivot_longer(cols=num_deaths_c:num_deaths_e, names_to="var", values_to="val")%>%
  group_by(lab2,var)%>%
  dplyr::summarise(death_med=median(val),
            death_25 = quantile(val, probs=0.25),
            death_75 = quantile(val, probs=0.75))%>%
  left_join(data.frame(var =c("num_deaths_c","num_deaths_a","num_deaths_e"),
                       age_grp = c("Child","Adult","Adult >50 yr")))%>%
  mutate(age_grp = factor(age_grp, level=c("Adult >50 yr","Adult","Child")))

death_e <- age_death %>%
        filter(var=="num_deaths_e")

p12o <- death_e%>%
  filter(var=="num_deaths_e")%>%
  ggplot()+
  geom_col(aes(x=lab2,y=death_med), fill="#006D2C", width=0.7, alpha=0.55)+
geom_errorbar(data=death_e, aes(x=lab2, ymin=death_25, ymax=death_75), width=0.3, size=0.7, color="gray50")+
  coord_flip()+
 theme_classic()+
ylab("Deaths")+xlab("")+ggtitle("10-yr cumulative deaths (older adults)")+
    theme(plot.title = element_text(size=14),
                      axis.text.x = element_text(size=13),
                      axis.text.y = element_text(size=11, hjust=1),
                      axis.title = element_text(size=13),
                     legend.position="right")+
    theme_frame

png("0_plot/res_older_randtime.png", width = 12,height = 4,units="in",res=500)
as_ggplot(arrangeGrob(p11o,p12o,nrow=1,ncol =6, layout_matrix=rbind(c(1,1,1,2,2,2))))
dev.off()

```


## NNT and age-specific deaths for all age groups
```{r}
#png("nnt_box_Rrand_lo_violin.png", width = 10,height = 5,units="in",res=400)
p11 <- nnt_main%>%
  filter(nnt >0)%>%
  left_join(scen_lab)%>%
  filter(!scen%in%c("No vax"))%>%
  ggplot(aes(x=factor(lab2), y=nnt, fill=lab2, text=lab2))+
  scale_y_log10()+
  geom_violin(width=1, size=0.2)+
  scale_fill_manual(values = rev(pal1))+
  scale_color_manual(values=rev(pal1))+
  #scale_fill_viridis(discrete=T, option="G")+
  #scale_color_viridis(discrete=T, option="G")+
  theme_bw()+
  theme(axis.text.x = element_text(vjust=0.8, hjust=0.5, size=11),
        axis.text.y = element_text(size=11),
        axis.title = element_text(size=12),
        plot.title = element_text(size=12),
        plot.margin = unit(c(-0.5,0,0,0.1), 'lines'),
        legend.position="none")+
  theme(panel.background = element_rect(fill = "white", colour = "black",size = 0.7, linetype = "solid"),
        panel.grid.major = element_line(size = 0.0001, linetype = 'solid',colour = "white"),
        panel.grid.minor = element_line(size = 0.0001, linetype = 'solid',
                                colour = "white"))+
  coord_flip()+
  ylab("No. of doses needed to avert one death")+xlab("Vaccination timing")+
  ggtitle("Number of vaccine doses needed to avert one death")
#dev.off()

##Age-specific death distribution by vax scenario
age_death <- nnt_main %>%
  left_join(scen_lab)%>%
  #filter(!scen%in%c("No vax"))%>%
  select(lab2, num_deaths_c:num_deaths_e)%>%
  pivot_longer(cols=num_deaths_c:num_deaths_e, names_to="var", values_to="val")%>%
  group_by(lab2,var)%>%
  summarise(death_med=median(val),
            death_25 = quantile(val, probs=0.25),
            death_75 = quantile(val, probs=0.75))%>%
  left_join(data.frame(var =c("num_deaths_c","num_deaths_a","num_deaths_e"),
                       age_grp = c("Child","Adult","Adult >50 yr")))%>%
  mutate(age_grp = factor(age_grp, level=c("Adult >50 yr","Adult","Child")))

all_death <- nnt_main %>%
        left_join(scen_lab)%>%
        #filter(!scen%in%c("No vax"))%>%
        group_by(lab2)%>%
        summarise(death_25 = quantile(num_deaths, probs=0.25),
                  death_75 = quantile(num_deaths, probs=0.75))

p12 <- age_death%>%
  ggplot()+
  geom_col(aes(x=lab2,y=death_med, fill=age_grp), position= "stack", width=0.7, alpha=0.5)+
  scale_fill_manual(values = c("#006D2C","#66C2A4","#CCECE6"),
                     labels=c("Older \nadults","Adult","Child"))+
geom_errorbar(data=all_death, aes(x=lab2, ymin=death_25, ymax=death_75), width=0.3, size=0.7, color="gray50")+
  coord_flip()+
 theme_classic()+
            ylab("Deaths")+xlab("")+ggtitle("10-yr cumulative deaths")+
          theme(plot.title = element_text(size=12),
                      axis.text.x = element_text(size=11),
                      axis.text.y = element_text(size=11, hjust=1),
                      axis.title = element_text(size=12),
                     legend.position="right", legend.title = element_blank(), legend.text = element_text(size=11))+ theme(plot.margin = unit(c(-0.5,0.5,0,-0.7), 'lines'))+
  theme(panel.background = element_rect(fill = "white", colour = "black",size = 0.5, linetype = "solid"),
      panel.grid.major = element_line(size = 0.001, linetype = 'solid',colour = "white"),
        panel.grid.minor = element_line(size = 0.001, linetype = 'solid',
                                colour = "white"))

png("0_plot/res_waninghi_all.png", width = 14,height = 5,units="in",res=400)
as_ggplot(arrangeGrob(p11,p12,nrow=1,ncol =6, layout_matrix=rbind(c(1,1,2,2,2))))
dev.off()
```


##Cases per capita
```{r}
inc <- readRDS("0_res/1_inc_facet_comb100.RDS")
inc<-inc%>%filter(sero_thresh %in% c("0","0.5","0.65","0.8","Annual", "Biennial"))

med<- inc%>%group_by(date,sero_thresh)%>%
      summarise(med = median(val),
                prob_25 = quantile(val, probs=0.10),
                prob_75 = quantile(val, probs=0.90))

p1 <- med %>% ggplot()+
    geom_ribbon(aes(x=date, ymin=prob_25, ymax=prob_75, fill="Range"))+
     theme_bw()+geom_line(aes(x=date, y=med, colour = "Cases \n per 100"), size=0.6)+  

    scale_colour_manual("",values="#EF3B2C")+
    scale_fill_manual("",values="gray78")+
  #ggtitle("10-year epidemic projection")+
  xlab("") + ylab("Cases per 100")+
  facet_wrap(~sero_thresh, nrow=1)+
    theme(plot.title = element_text(size=14),axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      axis.text = element_text(size=11),
                      axis.text.y = element_text(size=11),
                      axis.title = element_text(size=12),
                      strip.text = element_blank(),
                      legend.text = element_text(size=12),
                      legend.position = "right",legend.title = element_blank())+
  theme(plot.margin = unit(c(-0.5,0.2,-0.5,1), "line"))+
  theme(panel.background = element_rect(fill = "white", colour = "black",size = 0.7, linetype = "solid"),
        panel.grid.major = element_line(size = 0.001, linetype = 'solid',colour = "white"),
        panel.grid.minor = element_line(size = 0.001, linetype = 'solid',
                                colour = "white"))


png("0_plot/inc_strip.png",width = 12,height = 5,units="in",res=400)
p1
dev.off()


```


## Sero facet wrap
```{r}
sero <- readRDS("0_res/1_sero_facet_comb100.RDS")
thresh_line <- data.frame(scen=c("No vax","50% thresh", "65% thresh","80% thresh","Annual","Biennial"),
                          sero_thresh = c("0","0.5","0.65","0.8","Annual","Biennial"),
                          thresh_num = c(NA,51,66,80,NA,NA))%>%
              mutate(scen = factor(scen, levels = c("No vax", "50% thresh", "65% thresh", "80% thresh", "Annual","Biennial")))

sero<-sero%>%filter(sero_thresh %in% c("0","0.5","0.65","0.8","Annual","Biennial"))
sero<-sero%>%pivot_longer(cols = sero_c:sero_e, names_to = "sero",values_to="val")

sero_med<- sero%>%group_by(date,sero_thresh,sero)%>%
      summarise(med = median(val),
                prob25 = quantile(val, probs=0.25),
                prob75 = quantile(val, probs=0.75)) %>%
      left_join(thresh_line %>%select(scen, sero_thresh))

sero_med <- sero_med%>%mutate(
              scen = factor(scen, levels = c("No vax", "50% thresh", "65% thresh", "80% thresh", "Annual","Biennial"))
              )
sero_range_c <- sero_med %>%filter(sero=="sero_c")
sero_range_a <- sero_med %>%filter(sero=="sero_a")
sero_range_e <- sero_med %>%filter(sero=="sero_e")
                

p2 <-  ggplot()+
      geom_ribbon(data=sero_range_c,aes(x=date, ymin=prob25, ymax=prob75), fill="gray78",alpha=0.5)+
      geom_ribbon(data=sero_range_a,aes(x=date, ymin=prob25, ymax=prob75), fill="gray78", alpha=0.5)+
      geom_ribbon(data=sero_range_e,aes(x=date, ymin=prob25, ymax=prob75), fill="gray78", alpha=0.5)+
      geom_line(data=sero_med,aes(x=date, y = med, col = sero),size=1)+       
      facet_wrap(~scen, nrow=1, scales="fixed")+
      ylim(0,100) +theme_bw()+
      scale_color_manual(values = c("#4292C6","#C6DBEF","#08306B"),
                                   labels=c("Adult",
                                            "Child",
                                            "Older \nadults"))+
        xlab("")+
                theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      axis.text.y = element_text(size=11),
                      strip.text = element_text(size=13),
                      legend.position = "right",legend.title = element_blank(), legend.text = element_text(size=12),
                      plot.margin = unit(c(0,0,-0.5,1), "line"))+
      geom_hline(data=thresh_line,aes(yintercept=thresh_num),linetype="dashed",size=0.6)+
  ylab("Seroprevalence\n by age(%)")+
  theme(panel.background = element_rect(fill = "white", colour = "black",size = 0.7, linetype = "solid"),
        panel.grid.major = element_line(size = 0.00001, linetype = 'solid',colour = "white"),
        panel.grid.minor = element_line(size = 0.00001, linetype = 'solid',
                                colour = "white"))

png("0_plot/sero_strip.png",width = 12,height = 5,units="in",res=400)
p2
dev.off()
```

```{r}
p3 <-ggarrange(p2,p1,ncol=1, align="v")



png("0_plot/fig2_hiwane.png", width = 11,height = 11,units="in",res=600)
as_ggplot(arrangeGrob(p3, p11o,p12o, nrow=7,ncol =2, 
                      layout_matrix=rbind(c(1,1), c(1,1),c(1,1),c(1,1),c(2,3),c(2,3),c(2,3))))
dev.off()


```

##NNT death tradeoff
```{r}
lab = c("Annual","Biennial","50%","55%", "60%", "65%","70%","75%","80%")

##Main one for output
nnt_death_trade <- nnt_main %>%
  filter(scen!="No vax")%>%
  ggplot(aes(x=num_deaths_e, y=nnt_e, col=scen))+
  scale_fill_manual(values = rev(pal),labels = lab)+
  scale_color_manual(values=rev(pal),labels = lab)+
  scale_y_log10()+
  #scale_color_viridis(discrete=T, option="G", direction=-1, alpha=1)+
  #scale_fill_viridis(discrete=T, option="G", direction=-1, alpha=0.5)+
  geom_point()+
  xlim(0,10000)+ylim(0,10000)+
  theme_bw() + xlab("Number of deaths among older adults")+ylab("Number needed to treat (NNT) among older adults")

png("0_plot/nnt_death_trade.png", width = 6,height = 4,units="in",res=300)
nnt_death_trade
dev.off()

## Other explorations

nnt_main <- nnt_main%>%mutate(yr = firstvax/365)
                     

p10 <- nnt_main%>%
  filter(!scen%in%c("No vax","ann_late","bi_late"))%>%
  ggplot(aes(x=yr, y=nnt, col=scen))+
  scale_color_manual(values = rev(pal1)[3:9])+
  geom_point()+
  #geom_point(aes(x=300,y=2190),colour="#FECC8FFF",size=6, shape=18)+
  #geom_point(aes(x=300,y=1689),colour="#FDE4A6FF",size=6, shape=18)+
  geom_point(aes(x=300/365,y=2190),colour="red",size=6, shape=18)+
  geom_point(aes(x=300/365,y=1689),colour="orange",size=6, shape=18)+
  geom_hline(yintercept =2190, color="red", linetype="dashed", size=0.8)+
  geom_hline(yintercept= 1689, color="orange",linetype="dashed",size=0.8)+
  scale_y_log10()+
  ylab("Number needed to treat (NNT) among older adults")+xlab("Year of first campaign")+
  theme_bw()

png("0_plot/scatter_yrfirst_nnt.png", width = 6,height = 4,units="in",res=300)
p10
dev.off()
```


## Yearly cumulative NNT
```{r}
viridis(20, alpha = 1, begin = 0, end = 1, direction = 1, option = "A")
pal1 <- c("#201321FF","#3C3162FF","#3B589AFF","#3485A5FF","#3CB2ADFF","#81D8B0FF","#DEF5E5FF","#FDE4A6FF","#FECC8FFF")

nnt_yr <- readRDS("0_res/nnt_main_wanehi_yr.RDS")
nnt1_yr<-readRDS("0_res/nnt1_main_wanehi_yr.RDS")


nnt_yr <- nnt_yr %>%filter(yr!=10)%>%
  group_by(scenarios, sweep_unique)%>%
  replace(is.na(.),0)%>%
  mutate(num_dose_roll = cumsum(num_dose))
nnt_yr_novax <- nnt_yr %>%filter(scenarios==0)%>%
                  ungroup()%>%
                  select(sweep_unique, yr, new_Deaths_e_roll, new_Deaths_tot_roll)%>%
                  rename("new_Deaths_e_roll_novax"="new_Deaths_e_roll")%>%
                  rename("new_Deaths_tot_roll_novax"="new_Deaths_tot_roll")

nnt_yr <- nnt_yr %>% left_join(nnt_yr_novax, by=c("sweep_unique"="sweep_unique","yr"="yr"))%>%
            mutate(nnt_e_yr = num_dose_roll/(new_Deaths_e_roll_novax-new_Deaths_e_roll),
                   nnt_tot_yr = num_dose_roll/(new_Deaths_tot_roll_novax-new_Deaths_tot_roll))%>%
            filter(scenarios!=0)

nnt1_yr <- nnt1_yr %>%filter(yr!=10)%>%
          group_by(scenarios, sweep_unique)%>%
          replace(is.na(.),0)%>%
          mutate(num_dose_roll = cumsum(num_dose))%>%
            left_join(nnt_yr_novax, by=c("sweep_unique"="sweep_unique", "yr"="yr"))%>%
            mutate(nnt_e_yr = num_dose_roll/(new_Deaths_e_roll_novax-new_Deaths_e_roll),
                   nnt_tot_yr = num_dose_roll/(new_Deaths_tot_roll_novax-new_Deaths_tot_roll))
  
nnt_yr_trade <- nnt_yr %>%
  mutate(scenarios = as.character(scenarios))%>%
  rbind(nnt1_yr)%>%
  mutate(yr1=yr+1)%>%
  group_by(yr1, scenarios)%>%
  dplyr::summarise(med = median(nnt_e_yr, na.rm=T))%>%
   mutate(scenarios = factor(scenarios,
          levels = c("ann_late","bi_late","0.5","0.55","0.6", "0.65","0.7","0.75","0.8")))%>%
  arrange(scenarios)%>%
  ggplot(aes(x=yr1, y=med, col=scenarios))+
  scale_fill_manual(values = rev(pal1),labels = lab)+
  scale_color_manual(values=rev(pal1),labels = lab)+
  scale_x_continuous(breaks = seq(from = 1, to = 10, by = 1))+
  #scale_color_viridis(discrete=T, option="G", direction=-1, alpha=1)+
  geom_line(size=1, linetype="dashed")+
  geom_point(size=2.5)+theme_bw()+
  theme(legend.title=element_blank(),
        legend.position = "none")+
  xlab("Year")+ylab("Cumulative NNT (median)")

png("0_plot/nnt_trade.png", width = 11,height = 4,units="in",res=600)
as_ggplot(arrangeGrob( nnt_yr_trade, nnt_death_trade,nrow=2,ncol =2, 
                      layout_matrix=rbind(c(1,2), c(1,2))))
dev.off()


```


